---
title: "RMarkdownClass"
author: "Gonchi"
date: "14 de enero de 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide 

Plain text

*italisised text*

**bold text**zv

`for (i %in% 1:10)`
xzcv
## My Title

- Bullet one
- Bullet two

1. Item a
2. Item b

### A top level subheading

#### A second level subheading


##MORE SLIDES

```{r, comment ="", echo= TRUE}
head(mtcars)

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Sl